### 2022-05-30 main/chapter_2ljets.tex
fill in strong context todos

Figure~\ref{fig:2ljets_strong_contours} \TODO{sentence}

\TODO{data driven backgrounds: flavour symmetry, photon method z+jets, 40GeV cut}

>>>>

To target its signal models, $\twoljets$-strong search defines seven
overlapping signal regions.
Three target on-shell $Z^{(*)}$ models by selecting $\mll$ close to $m(Z)$,
and the others are binned in $\mll$ to give broad sensitivity to the various
kinematic edges across the grid of signal model parameters.

The largest Standard Model background to this search is dileptonic $\ttbar$,
in part because no $b$-jet veto is used.
All three signal models produce same-flavor lepton pairs, but $\ttbar$
produces same-flavor ($ee$/$\mu\mu$) and different-flavor ($e\mu$) pairs at
equal rates.
This difference in flavor symmetry is exploited to estimate backgrounds in
$\twoljets$-strong,
and its previous iterations~\cite{cms_susy_2016_strong_2l_run2_1}.
The estimate works by taking different-flavor data, weighting them by factors
to calibrate for differences in the leptons' reconstruction, and histogramming
them in same-flavour regions.
Simulations for $\ttbar$ and the smaller flavour symmetric backgrounds
$tW$, $WW$, and $\tau\tau$ are replaced by this estimate.

Post-fit results match the data to within $1$-sigma in all $\twoljets$-strong
regions.

Exclusion contours from the $\twoljets$-strong search are reproduced in
Figure~\ref{fig:2ljets_strong_contours}.
Besides their increased reach, the jagged edges to parts of these contour are
striking.
These arise from the combination of results from overlapping signal regions.
Because they overlap, they are not independent and cannot be trivially
combined.
Instead, each model in the signal grid is assigned to the signal region
with the ``best expected sensitivity'' by some measure.
An exclusion contour is constructed for each signal region, then those contours
are joined such that models assigned to each region use its corresponding
contour.

Personally, I find this hard to interpret.
If I had a pet theory which landed near to one of these sharp
region-transition edges, what should I make of these data?
Could some combination of the regions not have combined their information to
produce more precise contours?
Since model predictions change continuously, should our inferences not also?
To aid interpretations and to allow combinations of regions'
information, I chose to design the $\twoljets$-electroweak with only orthogonal
regions, and without any manual switching of regions between models.
